---
title: "Immigration and"
author: "Cheng Ren"
output: html_document
---


<h3> a function was written to combine all the data it is too slow to run here
```{r}
#function to paste year
# add_year<-function(name,year){
#   year<-rep(year, 9)
#   ny<-paste(name,year,sep="_")
#   return(ny)
# }
# #extract smaller table
# extr<-function(dataset){
#   colnames(dataset)<-tolower(names(dataset))
#   dataset_st<-dataset[,c('ein','name','address','city','state','zip','totrev','nteefinal','nteefinal1',
#                          'cont','secur',"salesexp","invinc","solicit","goods","grprof",
#                          "grrec","exps","fundbal","compens","fundfees","ass_boy","ass_eoy","liab_boy","liab_eoy",'progrev')]
#   colnames(dataset_st)<-c('ein','name','address','city','state','zip','totrev','ntee','ntee1',
#                           'tot_pub_sup','secur',"salesexp","invinc","solicit","goods","grprof",
#                           "grrec","exps","fundbal","compens","fundfees","ass_boy","ass_eoy","liab_boy","liab_eoy",'progrev')
#   return(dataset_st)
# }
# ## for loop
# filelist<-list.files(pattern = 'csv')
# i=1
# j=1988
# data_com<-data.frame()
# for( i in 1:22){
#   j=j+1
#   data_year<-read.csv(filelist[i])
#   data_year_st<-extr(data_year)
#   data_year_st$year<-j
#   data_com<-rbind(data_year_st,data_com)
#   #assign(paste('data_',j,'_st',sep=''),data_year_st)
# }
# ##name was changed according to IRS
# extr11<-function(dataset){
#   colnames(dataset)<-tolower(names(dataset))
#   dataset_st<-dataset[,c('ein','name','address','city','state','zip','totrev','nteefinal','nteefinal1',
#                          'cont','secur',"salesexp","invinc","lessdirfndrsng","goods","grprof",
#                          "grrec","exps","fundbal","compens","fundfees","ass_boy","ass_eoy","liab_boy","liab_eoy",'progrev')]
#   colnames(dataset_st)<-c('ein','name','address','city','state','zip','totrev','ntee','ntee1',
#                           'tot_pub_sup','secur',"salesexp","invinc","solicit","goods","grprof",
#                           "grrec","exps","fundbal","compens","fundfees","ass_boy","ass_eoy","liab_boy","liab_eoy",'progrev')
#   return(dataset_st)
# }
# ## for loop
# filelist<-list.files(pattern = 'csv')
# i=1
# j=2010
# data_com11<-data.frame()
# for( i in 23:length(filelist)){
#   j=j+1
#   data_year<-read.csv(filelist[i])
#   data_year_st<-extr11(data_year)
#   data_year_st$year<-j
#   data_com11<-rbind(data_year_st,data_com11)
#   #assign(paste('data_',j,'_st',sep=''),data_year_st)
# }
# #combine 
# data_comc <- rbind(data_com11,data_com)
```


```{r}
library(ggplot2)
library(dplyr)
library(tidycensus)
library(purrr)
library(tidyr)
```

```{r}
setwd('D:/API/bdr/add')
data_comc <- read.csv('data_comc.csv')
```


### 1.Explore the trends of nonprofit organizations


```{r}
names(data_comc)
table(data_comc$year)

#cl<-scale_color_manual(values=c("#FDB515", "#003262"))

increase<-data_comc%>% group_by(year) %>% tally()
  
p<-ggplot(increase, aes(x=year, y=n))+
  geom_point(color="#003262")+theme_minimal()+
  geom_smooth(color="#FDB515")+
  scale_y_continuous(labels = scales::comma)+
  ggtitle("Number of NPOs each year")
p
```

```{r}
increase2<-data_comc%>% group_by(year,ntee1) %>% tally()%>%filter(ntee1!="b")
p1<-ggplot(increase2, aes(x=year, y=n,group=ntee1,color=ntee1,label=ntee1))+
  geom_line()+theme_minimal()+
  scale_y_continuous(labels = scales::comma)+
  ggtitle("Number of NPOs each year by group")+
  geom_text(aes(x = 2016, y = 70000, label = "B", color = "B")) + 
  geom_text(aes(x = 2016, y = 50000, label = "P", color = "P"))+
  geom_text(aes(x = 2016, y = 45000, label = "A", color = "A"))+
  geom_text(aes(x = 2016, y = 38000, label = "N", color = "N"))+
  geom_text(aes(x = 2016, y = 30000, label = "X", color = "X"))+
  geom_text(aes(x = 2016, y = 25000, label = "E", color = "E"))
p1
```
<br>



<h5> Overall, the name of organizations was increasing in the past decades. Meanwhile, the top 6 organizations are type B(Education),P(Human Services),A(Arts, Culture & Humanities),N(Recreation & Sports),X(Religion-Related),E(Health Care). However, there are some human services or health service organizations are not in the same category but may serve the same group such as LGBTQ or immigrants. Thus, we need to figure out the algorithm to detect organization in other dimensions such as group of population.  



### 2.Trends of Immigrants
```{r}
years <- list(2009,2010,2011,2012,2013,2014,2015,2016,2017,2018)

multi_year <-
  map(
    years,
    ~ get_acs(
      geography = "state",
      variables = c(fborn = "B06001_049",
                    total_pop = "B01003_001"),
      year = .x,
      geometry = FALSE
    )) %>%
map2(years, ~ mutate(.x, id = .y))
```


```{r}
df_c=data.frame( multi_year[1])
for(i in 2:length(multi_year))
{
  df=data.frame(multi_year[i])
  df_c=rbind(df_c,df)
}
```

```{r}
df_fb<-df_c %>%
  filter(variable=='fborn')
df_total<-df_c %>%
  filter(variable=='total_pop')
```

```{r}
df_fb_total <- df_fb%>%group_by(id)%>%summarise(sum_pop=sum(estimate,na.rm = T))
p2<-ggplot(df_fb_total, aes(x=id, y=sum_pop))+
  geom_point(color="#003262")+theme_minimal()+
  geom_smooth(color="#FDB515")+
  scale_y_continuous(labels = scales::comma)+
  ggtitle("Number of immigrants each year")+
  xlab("Year")+ylab("#Population")
p2
```

```{r}
df_t_total <- df_total%>%group_by(id)%>%summarise(sum_pop=sum(estimate,na.rm = T))
df_t_total$per <- round(df_fb_total$sum_pop/df_t_total$sum_pop,4)*100
```

```{r}
p3<-ggplot(df_t_total, aes(x=id, y=per))+
  geom_point(color="#003262")+theme_minimal()+
  geom_smooth(color="#FDB515")+
  scale_y_continuous(labels = scales::comma)+
  ggtitle("Percentage of immigrants each year")+
  xlab("Year")+ylab("%Immigrants")
p3
```


##### In the past ten years, the number of immigrants and percentage of immigrants of total population are both increasing. Here we can see, there will be more demmands from immigrants as the population increases.If we divide the population in to different ethics immigrants, we can provide better personalized service. For example, if we can find all the immigrants realted organizations, we located their position. Meanwhile, there are also some open data related to ethic immigrants concentrated census tract. Then, we can undertsand the trends in each community and compare the mismatch between service providers and demmand. We can identify these organizaitions for immigrants and provide suggestions for some related organizations to expand their market in the right place, where might be a blue sea.  